Improving \textsl{Gaia} parallaxes with a data-driven model of the color--magnitude diagram

### 2017-02-22 paperDistance/paper.tex
note to self

We have shown that it is possible to obtain photometric parallaxes for
distant stars in the \gaia\ \tgas\ data without any use of physical stellar
models, nor models of the Milky Way.
We obtained these by building a data-driven model of the
color--magnitude diagram (\cmd) of the stars in the \tgas\ data set,
and using it as a prior pdf for Bayesian interences.
The posterior pdfs for distance that we obtain are, in general, much
narrower than the likelihood functions delivered by the
\gaia\ Mission, and therefore the distance estimates (or,
equivalently, parallax estimates) are much more precise.
It is not surprising that a Bayesian inference provides more
precise inferences than the likelihood function alone; Bayesian
inferences bring in new information that decrease variance (but
often introduce bias).
We have shown thatm, in addition to pure precision improvements, at
least some aspects of \emph{accuracy} have been improved as well, by
showing that the posterior distance estimates to stars in stellar
clusters are much more clustered than likelihood-based distance
estimates.

>>>>

We have shown that it is possible to obtain photometric parallaxes for
distant stars in the \gaia\ \tgas\ data without any use of physical stellar
models, nor models of the Milky Way.
We obtained these by building a data-driven model of the
color--magnitude diagram (\cmd) of the stars in the \tgas\ data set,
and using it as a prior pdf for Bayesian interences.
The posterior pdfs for distance that we obtain are, in general, much
narrower than the likelihood functions delivered by the
\gaia\ Mission, and therefore the distance estimates (or,
equivalently, parallax estimates) are much more precise.
It is not surprising that a Bayesian inference provides more
precise inferences than the likelihood function alone; Bayesian
inferences bring in new information that decrease variance (but
often introduce bias).
We have shown that, in addition to pure precision improvements, at
least some aspects of \emph{accuracy} have been improved as well, by
showing that the posterior distance estimates to stars in stellar
clusters [HOGG: Is this too general?] are much more clustered than likelihood-based distance
estimates.
